---
title: "Lucas Paiva's CV"
author: Lucas Ferreira Paiva
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: [ 'css/dd_cv.css', 'css/custom.css','resume']
    self_contained: true
#knit: pagedown::chrome_print      
---

```{r metathis, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "lucas-fpaiva/resumeL") %>% 
  meta_social(
    title = "Lucas Paiva CV",
    description = paste(
      "CV made with the packages RMarkdown, pagedown, datadrivencv."
    ),
    url = "https://lucaspaivacv.netlify.app",
    image = "https://avatars.githubusercontent.com/u/55860538?v=4",
    image_alt = paste(
      "Lucas Paiva CV"
    ),
    og_type = "website",
    og_author = "Lucas Ferreira Paiva"
  )
```

<!-- inicio academic icons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">
<!-- final academic icons -->

 
<!-- inicio font awesome -->
<script src="https://kit.fontawesome.com/c7b15a5f1b.js" crossorigin="anonymous"></script>
<!-- final font awesome -->


```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.R")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1YOb8Q9Z-QfYkGOR1XmYofMQuBKy-TwMRW0_vbNHT_-Q/edit?usp=sharing",
  pdf_mode = params$pdf_mode
)

CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
    <style>
    :root{
      --decorator-outer-offset-left: -6.5px;
}
    </style>")
}
```


Aside
===========================================================================
<center>
![Lucas Paiva](https://avatars.githubusercontent.com/u/55860538?v=4){width=100% style='border-radius: 50%;'}
</center>

### Contact

<center>
<a href='https://github.com/lucas-fpaiva' target='_blank'><i class="fa fa-github"></i></a> 
<a href='mailto:paiva.1996.lucas@gmail.com'><i class="fa fa-envelope"></i></a> <a href='https://orcid.org/0000-0003-4924-4666' target='_blank'><i class="fab fa-orcid"></i></a> 
<a href='http://lattes.cnpq.br/2288304608800735' target='_blank'><i class="ai ai-lattes"></i></a>
</center><br>

### Technical Skills

<boxText>Quantitative Data Analysis</boxText>

<boxText>Machine Learning</boxText> <boxText>Programming</boxText>

<boxText>Statistics</boxText> <boxText>Data Visualization</boxText>



### Code Skills

<boxText><i class="fab fa-python"></i>Python</boxText> <boxText><i class="fas fa-mountain"></i>Matlab</boxText> <boxText><i class="fas fa-feather"></i>LaTeX</boxText>

<boxText><i class="fas fa-code-branch"></i>Git</boxText> <boxText><i class="fab fa-github"></i>GitHub</boxText> <boxText><i class="fab fa-markdown"></i>Markdown</boxText>


### Soft Skills

<boxText>Teamwork</boxText> <boxText>Responsibility</boxText>

<boxText>Critical Thinking</boxText> 
<boxText>Collaboration</boxText>

<boxText>Research</boxText> <boxText>Time-Management</boxText>

### Languages

<boxText>Portuguese</boxText> <boxText>English</boxText> <boxText>Spanish</boxText>

### Hobbies and Interests

<boxText><i class="fas fa-volleyball"></i>Volleyball</boxText> <boxText><i class="fas fa-leaf"></i>Gardening</boxText>

<boxText><i class="fas fa-music"></i>Dancing</boxText> <boxText><i class="fas fa-handshake-angle"></i>Volunteering</boxText>

<boxText><i class="fas fa-screwdriver-wrench"></i>Repairing Things</boxText>

<br>

```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(params$pdf_mode){
  cat("View this CV online on [https://lucaspaivacv.netlify.app](https://lucaspaivacv.netlify.app)")
} else{ cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/lucas-fpaiva/resumeL/raw/master/index.pdf)")}
```

Main
==========================================================================

Lucas Ferreira Paiva {#title}
--------------------------------------------------------------------------


```{r}
cat('Motivated data scientist with 3+ years of experience. Passionate about building models that fix problems. I believe that a diversified training goes beyond technical knowledge, providing a more humanistic and integral vision.')
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```


Selected Projects {data-icon=laptop}
--------------------------------------------------------------------------

```{r}
CV %<>% print_section('projects')
```



\pagebreak

::: aside

Disclaimer {#disclaimer}
--------------------------------------------------------------------------
Made w/ [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](http://nickstrayer.me/datadrivencv/index.html). 

Source code: [github.com/lucas-fpaiva/resumeL](https://github.com/lucas-fpaiva/resumeL).

Last updated on `r Sys.Date()`.

:::


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------

```{r}
CV %<>% print_section('teaching_experience')
```



Selected Oral Communications {data-icon=microphone}
---------------------------------------------------------------------------

```{r}
CV %<>% print_section('oral_communications')
```


Scientific Publications {data-icon=book}
---------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```




